Points Above Replacement

### 2022-04-21 Code/NBAPARCode.Rmd
Add files via upload

```{r data, include=FALSE}
league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/League.csv', stringsAsFactors = TRUE, header = TRUE)
```

@@

```{r performing regression, echo=FALSE}
print('Regression of PAR(X) on VORP(Y)')
PARandVORP<-lm(scaledPAR~league$VORP)
summary(PARandVORP)
plot(league$VORP, scaledPAR)

@@

Plots
```{r plot1, echo = FALSE}
print('Plots of Multiple Regression with PAR as Y')
plot(multipleRegression)
```

>>>>

```{r data, include=FALSE}
league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/Data/League.csv', stringsAsFactors = TRUE, header = TRUE)
```

@@

```{r performing regression, echo=FALSE}
print('Regression of PAR(X) on VORP(Y)')
PARandVORP<-lm(scaledPAR~league$VORP)
summary(PARandVORP)

@@

Plots
```{r plot1, echo = FALSE}
print('Plots of Multiple Regression with PAR as Y')
plot(multipleRegression)

legend<-quantile(scaledPAR, probs = c(0, 0.5, 0.75, 0.9, 0.95, 1))
print("Breaking PAR into 5 groups")
print(legend)

plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR", main = "Value Over Replacement Player vs. Points Above Replacement")
plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR", main = "Win Shares vs. Points Above Replacement")
plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR", main = "Box Plus Minus vs. Points Above Replacement")
plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR", main = "Player Efficiency Rating vs. Points Above Replacement")
```
